A Methodology to Define QoS and SLA Requirements in Service Choreographies

### 2012-08-08 articles/CAMAD2102/article-version2.tex
adding Paper-CAMAD-Alfonso-IMEUSP and fixing somethings

 \item Simulations of scenarios, one with a minimum configuration of failures and another with a higher possibility of failure. Simulations
  are used because choreographies in the real world represent complex processes which generate complex petri nets with many states 
  that difficult analytical evaluations \cite{Oliveira2009}.

@@

%Nesta seção são aplicados os passos descritos da nossa abordagem no cenário de exemplo da Seção \ref{serviceChoreography} .
To attest the efficacy of our proposal, in this section all the steps of our methodology are performed. The choreography
 presented in Figure~\ref{fig:choreographyExample} is used in the process because that scenario is simple in order to show and understand better the
 purposed methodology, and includes at least one element of three choreography  BPMN types (task, gateways and events). Each one of the
 next subsections describes one of the three steps of  the proposal defined in the Section~\ref{sec:proposta}.

>>>>

 \item Simulations of scenarios, one with a minimum configuration of failures and another with a higher possibility of failure. Simulations
  are used because choreographies in the real world represent complex processes, which generate complex petri nets with many states 
  that become in difficult analytical evaluations \cite{Oliveira2009}.

@@

%Nesta seção são aplicados os passos descritos da nossa abordagem no cenário de exemplo da Seção \ref{serviceChoreography} .
To attest the efficacy of our proposal, in this section all the steps of our methodology are performed. The choreography
 presented in Figure~\ref{fig:choreographyExample} is used in the process  because that scenario is simple in order to show and understand better the
 proposed methodology, and includes at least one element of three choreography  BPMN types (task, gateways and events). Each one of the
 next subsections describes one of the three steps of  the proposal defined in the Section~\ref{sec:proposta}.
